---
title: "Wine Quality Data"
author: "Harsh Mehta"
date: "2022-11-30"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

## Exploring the Data

```{r include=FALSE}
df <-read.csv("C:\\Users\\91797\\Downloads\\Wine Quality Data.csv")
library(dplyr)
library(tidyverse)
```

```{r}
str(df)
head(df)
```

The df data frame consist of 6465 Columns and 15 Rows

-   type

-   fixed acidity

-   volatile acidity

-   citric acid

-   residual sugar

-   chlorides

-   free sulfur dioxide

-   total sulfur dioxide

-   density

-   pH

-   sulphates

-   alcohol

-   quality

-   Bill Of Materials(Cost for Making the wine)

-   Cost of storage

-   Price

## **Cleaning the Data**

The Data frame 'df' consist tibbles with the value '0'. To get rid of this data we will use `na.omit()` Function. The new data frame now only consists of 6308 row.

```{r}
df[df == 0] <- NA
winequality<-na.omit(df)
dim(winequality)
```

To understand the data more clearly we will add Two more columns to the data Indicating Profit and Total Cost

```{r}
total_cost <- winequality$BillOfMaterials + winequality$StorageCost  
winequality <- winequality %>%
  add_column(total_cost)

profit <- winequality$Price -winequality$total_cost
winequality <- winequality %>%
  add_column(profit)
```

#### Questions

Q1 -\> What is the difference between different types of wines?

Q2 -\> What are the costs and different attributes of that cost?

Q3 -\> What determines the quality and what does the ideal wine look like?

Q4 -\> What factors determines the price/profit of the wine and what is the percentage of the profit generated?

Q5 -\> Is there any Correlation between different attributes of the wines?

#### Q1 -\> What is the difference between different types of wines?

```{r echo=TRUE}
library("ggthemes")
library("gridExtra")
library(ggplot2)
g1 <- ggplot(winequality) +
  aes(x = type, y = alcohol, fill = type) +
  geom_bar(position="dodge",stat="summary",fun="mean") +
  
  labs(title = "Average Alcohol in diifrent types of wine",
       x = "type", y = "Mean alcohol")+
  theme_economist()

g2 <-  ggplot(winequality) +
  aes(x = type, y = pH, fill = type) +
  geom_bar(position="dodge",stat="summary",fun="mean") +
  
  labs(title = "Average pH in diifrent types of wine",
       x = "type", y = "Mean pH")+
  theme_economist()

g3 <- ggplot(winequality) +
  aes(x = type, y = fixed.acidity, fill = type) +
  geom_bar(position="dodge",stat="summary",fun="mean") +
  
  labs(title = "Average acidity in diifrent types of wine",
       x = "type", y = "Mean acidity")+
  theme_economist()

g4 <- ggplot(winequality) +
  aes(x = type, y = residual.sugar, fill = type) +
  geom_bar(position="dodge",stat="summary",fun="mean") +
  
  labs(title = "Average sugar in diifrent types of wine",
       x = "type", y = "Mean sugar")+
  theme_economist()

g5 <- ggplot(winequality) +
  aes(x = type, y = quality, fill = type) +
  geom_bar(position="dodge",stat="summary",fun="mean") +
  
  labs(title = "Average quality diifrent types of wine",
       x = "type", y = "Mean quality")+
  theme_economist()

g6 <-ggplot(winequality) +
  aes(x = type, y = sulphates, fill = type) +
  geom_bar(position="dodge",stat="summary",fun="mean") +
  
  labs(title = "Average sulphates in diifrent types of wine",
       x = "type", y = "Mean sulphates")+
  theme_economist()

g7 <-ggplot(winequality) +
  aes(x = type, y = Price, fill = type, fill = type) +
  geom_bar(position="dodge",stat="summary",fun="mean") +
  
  labs(title = "Average price of diifrent types of wine",
       x = "type", y = "Mean price")+
  theme_economist()
g8 <-ggplot(winequality) +
  aes(x = type, y = total_cost, fill = type) +
  geom_bar(position="dodge",stat="summary",fun="median") +
  
  labs(title = "Median cost of diifrent types of wine",
       x = "type", y = "Mean cost")+
  theme_economist()

```

```{r}
grid.arrange(g1, g2, ncol = 2)
grid.arrange(g5, g6, ncol = 2)
grid.arrange(g3, g4, ncol = 2)
grid.arrange(g7, g8, ncol = 2)
```

By Studying the Average contents of Red and White Wine We can Conclude that:

-   White wine contains more sugar then red wine

-   Red wine contains more sulfates then the white wine

-   Red wine is slightly more acidic in nature

#### Q2 -\> What are the costs and different attributes of that cost?

The total cost is based on the sum of of Bill of Materials and the Storage Cost. To explore this columns we will plot A histogram and will also see its probability density. The generic function `hist` computes a histogram of the given data values. `density()` function computes kernel density estimates.

```{r}
hist(winequality$BillOfMaterials,freq = FALSE, col=rgb( 1,.25,.25, .2))
lines(density(winequality$BillOfMaterials), col="darkgoldenrod1", lwd=2)
hist(winequality$StorageCost, freq = FALSE, col=rgb( 1,.25,.25, .2))
lines(density(winequality$StorageCost), col="darkgoldenrod1")

```

We will see the Correlation of the attributes and find out what factors affect the cost. `corr_var()`function correlates a whole dataframe with a single feature. It automatically runs `ohse` (one-hot-smart-encoding) so no need to input only numerical values.

```{r}
library('lares')
corr_var(winequality, 
         BillOfMaterials, 
)
corr_var(winequality, 
         StorageCost
)
```

-   Majority of the wines has the cost of ingredients from 500 to 700 rupees

-   Majority of the wine has the storage cost of 225 to 325 rupees

-   The major factor affecting the cost is the quality of the wine i.e the higher the rating of the wine, Higher its cost.

#### Q3 -\> What determines the quality and what does the ideal wine look like?
Lets Explore the quality of wine by type.
```{r}
ggplot(winequality, aes(x = as.factor(winequality$type))) +
  geom_density(aes(fill = as.factor(quality)), alpha = 0.2)+  labs(x="Wine Color ", y= "Density")
```

We will see the Correlation of the attributes and find out what factors affects the quality.

```{r}
corr_var(winequality, 
         quality)
```

Using `ggpolt()` we will plot some graphs to study the correlations.

```{r}
g9 <-ggplot(winequality, aes(x = alcohol, y = quality, col = type))+
  geom_point(aes(shape = type))+
  labs(title = "Alcohol VS Quality",
          x = "Alcohol", y = "Quality")
g9 + theme_economist()

g10 <- ggplot(winequality, aes(winequality$Price, winequality$quality)) + labs(title = "Price VS Quality", x = "Price", y = "Quality") + geom_line(colour = "#0c4c8a", size = 2) + theme_economist()

g11 <- ggplot(winequality, aes(winequality$total_cost, winequality$quality)) + labs(title = "Cost VS Quality",cx = "Cost", y = "Quality") + geom_line(colour = "#87728c", size = 2) + theme_economist()
grid.arrange(g10, g11, ncol = 2)
```

We will make a different data frame with highest rated quality wine and observe it

```{r}
library(summarytools)
max(winequality$quality)
Ideal_Wine <- filter(winequality, winequality$quality == 9)
Ideal_Wine_Summarry <- summarytools::descr(Ideal_Wine, round.digits = 2, transpose = TRUE)
Ideal_Wine_Summarry
```

-   All the highest rated wines are white

-   The price and cost of the highest rated wines are also very high

#### Q4-\> What factors determines the price/profit of the wine and what is the percentage of the profit generated?

We will see the Correlation of the attributes and find out what factors affect the price and profit.

```{r}
corr_var(winequality, 
         Price)
corr_var(winequality, 
         profit)
```

Profit persent with the different attributes.

```{r}
Avereage_Profit_Persent <- mean(winequality$profit)*100/mean(winequality$Price)
Avereage_Profit_Persent
min_Profit_Persent <- min(winequality$profit)*100/mean(winequality$Price)
min_Profit_Persent
Max_Profit_Persent <- max(winequality$profit)*100/mean(winequality$Price)
Max_Profit_Persent
```

We will now compute the top most profitable wine and analyze its summary and correlation

```{r}
Max_Profit<-slice_max(winequality, n = 10, winequality$profit)
corr_var(Max_Profit, 
         profit)
Max_profit_Wine_Summarry <- summarytools::descr(Max_Profit, round.digits = 4, transpose = TRUE)
Max_profit_Wine_Summarry
```

We will now compute least profitable wine and analyze its summary and correlation

```{r}

Min_Profit<-slice_min(winequality, n = 10, winequality$profit)
corr_var(Min_Profit, 
         profit)
Min_profit_Wine_Summarry <- summarytools::descr(Min_Profit, round.digits = 4, transpose = TRUE)
Min_profit_Wine_Summarry
```

-   The gross profit percent lies between 25% to 87%.

-   The least profitable wines have a very high pH value.

-   The factor affecting the price and profit most is quality.

#### Q5-\> Is there any Correlation between different attributes of the wines?

**`cov()`** form the variance-covariance matrix calculate the covariance of the numeric values . **`cor()`** forms the correlation matrix.
The `unlist()` function and `lapply()` is used to select only numeric values from the data set.

```{r}
cov_matrix <- cov(winequality [,unlist(lapply(winequality, is.numeric))])
cov_matrix

cor_matrix <- cor(winequality[,unlist(lapply(winequality, is.numeric))])
cor_matrix

```

To plot the correlation we will use `corrplot()` library.

```{r}
library(corrplot)
corrplot(cor_matrix, method = 'color', order = 'alphabet')
```

As per the analysis we can concluded that the alcohol is inversely correlated to density. To dig deep into it we will only focus on correlation matrix of alcohol.

The `lm()` function is used to fit linear models to data frames. After doing so we will also summarize it.

```{r}
alcohoal_density = lm(winequality$alcohol~winequality$density)
summary(alcohoal_density)
```

Also we will plot a linear distribution graph to understand the distribution

```{r}
ggplot(winequality, aes(x = alcohol, y = density)) + geom_point() + geom_smooth(method = "lm")
```

-   The more the Alcohol contents the lesser the density of the alcohol

-   There are few outlines in density column
